\bf Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-10 acl.2016/amta2016.tex
whatever

Figure~\ref{fig:mempool} compares the decoding speed for Moses and our decoder, using the same models, parameters and test set. Our decoder is over 3 times faster with one thread, and 4.7 times faster using all cores. Like Moses, performance actually worsens after approximately 15 threads, however, the problem is not as pronounced. This gives us a better foundation on which to build further innovations for fast, multi-core decoding.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{mempool.png}} 
\end{tabular}
\caption{Decoding time of Moses and our decoder, using the same models}
\label{fig:mempool}
\end{figure}

>>>>

Figure~\ref{fig:mempool} compares the decoding speed for Moses and our decoder, using the same models, parameters and test set. Our decoder is over 3 times faster with one thread, and 5.0 times faster using all cores. However, like Moses, performance actually worsens after approximately 15 threads. %, however, the problem is not as pronounced. This gives us a better foundation on which to build further innovations for fast, multi-core decoding.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{mempool.png}} 
\end{tabular}
\caption{Decoding speed of Moses and our decoder, using the same models}
\label{fig:mempool}
\end{figure}
